\cvsection{Professional Background}

\begin{cventries}

\cventry
{Human Rights Activist}
{Volunteering Work at Several Groups}
{Munich, Germany}
{2017-}
{
\begin{cvitems}
  \item Consultant, Doctor Level. Working Hours: 20h weekly.
  \item Activities: Listening to victims of human rights violations, Social and legal advice and Analysis of Court proceedings.
  \item Groups: Mulheres Unidas com o Brasil, Coletivo Resistência Democrática, Revibra and CABE.
\end{cvitems}
}

\cventry
{Group Coordinator}
{University of Campinas, UNICAMP, Brazil}
{Campinas, São Paulo}
{2017-}
{
\begin{cvitems}
  \item Study Group in Mobilization of Law. With Celly Cook Inatomi (Founder).
\end{cvitems}
}

\cventry
{Professor in Law}
{Mackenzie Presbyterian University}
{Campinas, São Paulo}
{2015-2016}
{
\begin{cvitems}
  \item Assistant Professor, Master Level. Working Hours: 40h weekly.
  \item Subject Matters: Constitutional Process and Control of Constitutionality, Fundamental Rights, Introduction to the Study of Law, Constitutional Theory, Human Rights.
\end{cvitems}
}

\cventry
{Researcher}
{National Commission of Truth (CNV), Brazil}
{São Paulo, São Paulo}
{2013-2014}
{
\begin{cvitems}
  \item Functional Placement: Researcher. Working hours: 40h weekly.
  \item Worked in the Dictatorship and Gender working group. Activities: Reporting on human rights, literature review on dictatorship and human rights, listening to survivors of serious human rights violations, searching public archives, filling out forms and qualitative data analysis.
\end{cvitems}
}

\cventry
{Researcher}
{Center for Contemporary Culture Studies (CEDEC), Brazil}
{São Paulo, São Paulo}
{2009 - 2014}
{
\begin{cvitems}
  \item Type of contract: Researcher Collaborator. Working Hours: 2h weekly.
\end{cvitems}
}

\cventry
{Researcher}
{National Institute of Studies on the United States (INEU), Brazil}
{São Paulo, São Paulo}
{2009 - 2014}
{
\begin{cvitems}
  \item Working Hours: 2h weekly.
\end{cvitems}
}

\cventry
{Teacher (Intern)}
{University of Campinas, UNICAMP, Brazil}
{Campinas, São Paulo}
{2008; 2011}
{
\begin{cvitems}
  \item Teaching Internship, PED B. Subject: Comparative Political Systems. Advisor: Andrei Koerner. Took half of lectures (2008).
  \item Teaching Internship, PED C. Subject: Politics IV: Liberal Political Thought. Advisor: Andrei Koerner (2011).
\end{cvitems}
}

\cventry
{Researcher}
{University of Londrina, UEL, Brazil}
{Londrina, Paraná}
{2007 - 2016}
{
\begin{cvitems}
  \item Functional Placement: Researcher-collaborator.
\end{cvitems}
}

\end{cventries}
